Exploratory Figures

### 2024-06-18 Manuscript Analysis/exploratory_figures.Rmd
LE corr plot

ple_data <- rio::import("Cleaned Data/cleaned_ple_data.csv") |>
  dplyr::left_join(phrase_acc, by = c("subject", "trial")) |>
  dplyr::mutate(speaker = factor(speaker, levels = c("Control", "ALS")),
                trial_c = trial - 6,
                rep_acc = factor(rep_acc, levels = c("accurate", "inaccurate"))) |>
  dplyr::filter(!is.na(rep_acc)) |>
  dplyr::filter(effort_rating > 0)

@@

@@

@@

>>>>

ple_data <- rio::import("Cleaned Data/cleaned_ple_data.csv") |>
  dplyr::left_join(phrase_acc, by = c("subject", "trial")) |>
  dplyr::mutate(speaker = factor(speaker, levels = c("Control", "ALS")),
                trial_c = trial - 6,
                rep_acc = factor(rep_acc, levels = c("accurate", "inaccurate"))) |>
  dplyr::filter(!is.na(rep_acc)) |>
  dplyr::filter(effort_rating > 0) |>
  dplyr::filter(effort_rating <= 7)

@@

## Repeated Measures Correlation

### Overall Correlation

@@

peak_pupil <- peak_pupil |>
  dplyr::select(subject, trial_c, speaker, peak_pupil, intel)

ple_data <- ple_data |>
  dplyr::select(subject, trial_c, speaker, effort_rating, intel)

corr_df <- dplyr::left_join(peak_pupil, ple_data, by = c("subject", "trial_c", "speaker", "intel"))

rmcorr::rmcorr(subject, peak_pupil, effort_rating, corr_df)

@@

#### Plot

corr_df |>
  dplyr::mutate(speaker = factor(speaker, levels = c("Control", "ALS"),
                                   labels = c("Neurotypical", "ALS")),
                color = ifelse(speaker == "ALS", my_pal[5], my_pal[1])) |>
  ggplot() +
  aes(x = effort_rating,
      y = peak_pupil) +
  geom_line(method = "lm", stat = "smooth", aes(group = subject), alpha = .3) +
  geom_line(stat = "smooth", method = "lm", size = 2) +
  labs(x = "Perceived Listening Effort Rating", 
       y = "Peak Pupil Dilation (Arbitrary Units)") +
  coord_cartesian(xlim = c(1, 7)) +
  theme_bw() +
  theme(legend.position = "bottom",
        aspect.ratio = 1)

ggsave("Figures/effort_corr.png", plot = last_plot())

corr_df |>
  dplyr::mutate(speaker = factor(speaker, levels = c("Control", "ALS"),
                                   labels = c("Neurotypical", "ALS")),
                color = ifelse(speaker == "ALS", my_pal[5], my_pal[1])) |>
  ggplot() +
  aes(x = effort_rating,
      y = peak_pupil,
      color = speaker) +
  geom_line(method = "lm", stat = "smooth", aes(group = subject), alpha = .3) +
  geom_line(stat = "smooth", method = "lm", size = 2) +
  labs(x = "Perceived Listening Effort Rating", 
       y = "Peak Pupil Dilation (Arbitrary Units)") +
  facet_wrap("speaker") +
  coord_cartesian(xlim = c(1, 7)) +
  theme_bw() +
  theme(legend.position = "bottom",
        aspect.ratio = 1) +
  scale_color_manual(values = c(my_pal[1], my_pal[5]))

ggsave("Figures/effort_corr_speaker.png", plot = last_plot())
